Changelog

### 2021-05-20 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsection{Attack Models}
Previous work~\cite{182946} classifies side-channel attacks into three types based on the type of information that an attacker can learn during the attack.
\subsubsection*{Timing-based Attacks}
In timing-based attacks, an adversary can monitor the execution time of a victim program. It could be the overall execution time or the execution time of some interesting points (e.g., a function).  The execution time is correlated to some events (e.g., cache hits and misses, page faults, the number of instructions). Examples of those attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein's attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
\subsubsection*{Access-based Attacks}
In access-based attacks, an adversary can probe one time only after the termination of the victim program. The attacker can learn the memory addresses that are accessed during the execution. For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss. Since the attacker can probe the victim program after the execution, the attacker does not know the order of memory accesses. Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC cache). Examples of those attacks include cache template attacks~\cite{191010}, Prime+Probe attacks~\cite{liu2015last}, and Flush+Reload attacks~\cite{yarom2014flush+}.
\subsubsection*{Trace-based Attacks}
In trace-based attacks, an adversary can probe the victim program at any point. The attacker can learn the order of memory accesses. Suppose the victim program has two functions \textsf{a} and \textsf{b}. In an access-based attacks, the attacker can only learn both \textsf{a} and \textsf{b} are executed. In a trace-based attack, the attacker can know the execution sequence of two functions (e.g., $aabbb$). Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to the category where a malicious operating system can interrupt the victim application and probe the program at any time. In general, the trace-based attack has the strongest assumption about the threat model,  but it can retrieve more information compared to the other two types of attacks.
\subsection{Target Applications}
There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks. Most early work targeted retrieving encryption keys from cryptography libraries. In recent years, researchers start to focus on more general and diverse applications. In summary,  the target applications of current side-channel attacks can be classified into three categories.

@@

The first side-channel attack on cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the simple modular exponentiation algorithm function in many algorithms (Diffie-Hellman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.  Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.  Note that cryptography libraries usually have several implementations for some ciphers.
For example, AES can have more than five different implementations in OpenSSL. Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them. The reference implementation usually adopts T-Tables and S-Tables to speed up the computation. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side-channel mitigated versions. However, recent studies also show those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}. The situation is even worse for asymmetric ciphers (e.g., Diffie-Hellman, RSA, ECDSA). Those ciphers have a lot of big number calculations. It is hard to implement those calculations to be completely side-channel resistant. Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of those ciphers. There are two common countermeasures to mitigate side-channel attacks in cryptography libraries. The first approach is to adopt constant time operation when computing the secret data.  It is hard to migrate all the code into a constant-time implementation. The second approach is to use blinding to reduce the information that an attacker can retrieve. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks.

>>>>

\subsection{Attack Models}
Previous work~\cite{182946} classifies side-channel attacks into three types based on the type of information that an attacker can learn during the attack.
\subsubsection*{Timing-based Attacks}
In timing-based attacks, an adversary can measure and compare the execution time of victim programs. It could be the overall execution time or the execution time of some interesting points (e.g., a function).  The execution time is correlated to some events (e.g., cache hits and misses, page faults, the number of instructions). Timing-based attacks are perilous because these attacks are able to be carried out remotely over the networks remotely~\cite{brumley2005remote}. Examples of these attacks include remote timing attacks~\cite{brumley2005remote}, Bernstein's attack on AES~\cite{bernstein2005cache}, and Kocher’s original attack~\cite{kocher1996timing} from CRYPTO 96.
\subsubsection*{Access-based Attacks}
In access-based attacks, an adversary can learn the memory addresses that are accessed during the execution after the termination of the victim program. 
For example, a cache-based channel attack can know which memory access incurs a cache hit and which memory access incurs a cache miss to infer addresses that the victim program accesses. Since the attacker can probe the victim program after the execution, the attacker does not know the order of memory accesses. Access-based attacks often happen in the cloud computing environment when the attacker and victim share the same hardware (e.g., LLC cache). Examples of those attacks include cache template attacks~\cite{191010}, Prime+Probe attacks~\cite{liu2015last}, and Flush+Reload attacks~\cite{yarom2014flush+}.
\subsubsection*{Trace-based Attacks}
In trace-based attacks, an adversary can interrupt and  probe the victim program at any point. The attacker can learn the order of memory accesses. Suppose the victim program has two functions \textsf{a} and \textsf{b}. In an access-based attacks, the attacker can only learn both \textsf{a} and \textsf{b} are executed. In a trace-based attack, the attacker can know the execution sequence of two functions (e.g., $\mathtt{aabbb}$). Controlled-channel attacks~\cite{moghimi2020copycat, xu2015controlled} belong to this category where a malicious operating system can interrupt the victim application and probe the program at any time. In general, the trace-based attack has the strongest assumption about the threat model,  but it can retrieve more information compared to the other two types of attacks.
\subsection{Target Applications}
There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks. Most early works targeted retrieving encryption keys from cryptography libraries. In recent years, researchers start to focus on more general and diverse applications. In summary,  the target applications of current side-channel attacks can be classified into three categories.

@@

The first side-channel attack on cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the simple modular exponentiation algorithm function in many algorithms (Diffie-Hellman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.  Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.  Note that cryptography libraries usually have several implementations for some ciphers.
For example, AES can have more than five different implementations in OpenSSL. Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them. The reference implementation usually adopts T-Tables and S-Tables to speed up the computation. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side-channel mitigated versions. However, recent studies also show those versions (e.g., AES-NI) also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}. The situation is even worse for asymmetric ciphers (e.g., Diffie-Hellman, RSA, ECDSA). These ciphers have a lot of big number calculations. It is hard to implement those calculations to be completely side-channel resistant. Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private key of those ciphers. There are two common countermeasures to mitigate side-channel attacks in cryptography libraries. The first approach is to adopt constant time operation when computing the secret data.  It is hard to migrate all the code into a constant-time implementation. The second approach is to use blinding to obfuscate the information that an attacker can retrieve. Side-channel attacks allow an adversary to retrieve information by measuring something other than the program's output itself. Binding values can alter the input to some unpredictable data and introduce the randomization to the execution. However, the binding value can also be retrieved by an attacker through other methods, including side-channel attacks. An attacker can launch an attack to retrieve the binding value to recover the secret input.
